\section{Quiz}
\subsection{Manage identity and access}
As an enterprise or software-as-a-service (SaaS) developer you which to build an application which allows users to sign in using their Personal Microsoft accounts. Which Microsoft Identity platform library provides authentication tools for Personal Microsoft accounts?
\begin{todolist}
\item Microsoft Authentication Library (MSAL)
\item Azure AD Authentication Library (ADAL)
\item .NET DotNetOpenAuth (OAuth)
\item Microsoft Active Directory Library (MADL)
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}
An application which allows users to update their contact information, is created utilising the delegated permission scheme. Can the current user signed in, Bob from HR, update the contact information of his colleague Alice, using the application? \textit{The application has the User.ReadWrite.All delegated permission in Microsoft Graph.}
\begin{todolist}
\item Yes. The effective permissions granted by the application allows signed-in user the ability to update all users.
\item No. The effective permissions granted by the application does not allow signed-in user the ability to update all users.
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}
As part of a merger is is necessary to transfer the billing ownership of several user accounts. Which of the these account types can have their billing ownership transferred.
\begin{todolist}
\item Azure in Open (AIO)
\item Visual Studio Enterprise (MPN) subscribers
\item Visual Studio Professional
\item Microsoft Partner Network
\item Free Trial
\item Pay-As-You-Go
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}

\vspace{1cm}
\textcolor{red}{\textit{Create additional questions from \href{https://docs.microsoft.com/en-us/azure/active-directory/develop/v2-permissions-and-consent\#using-the-admin-consent-endpoint}{https://docs.microsoft.com/en-us/azure/active-directory/develop/v2-permissions-and-consent\#using-the-admin-consent-endpoint}}}