\section{Quiz (with answers)}
\subsection{Manage identity and access}
As an enterprise or software-as-a-service (SaaS) developer you which to build an application which allows users to sign in using their Personal Microsoft accounts. Which Microsoft Identity platform library provides authentication tools for Personal Microsoft accounts?
\begin{todolist}
\item[\correct] Microsoft Authentication Library (MSAL)
\item[\incorrect] Azure AD Authentication Library (ADAL)
\item[\incorrect] .NET DotNetOpenAuth (OAuth)
\item[\incorrect] Microsoft Active Directory Library (MADL)
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}
An application which allows users to update their contact information, is created utilising the delegated permission scheme. Can the current user signed in, Bob from HR, update the contact information of his colleague Alice, using the application? \textit{The application has the User.ReadWrite.All delegated permission in Microsoft Graph.}
\begin{todolist}
\item[\incorrect] Yes The effective permissions granted by the application allows signed-in user the ability to update all users. 
\item[\correct] No. The effective permissions for the application does not allow signed-in user the ability to update all users.
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}
As part of a merger is is necessary to transfer the billing ownership of several user accounts. Which of the these account types can have their billing ownership transferred.
\begin{todolist}
\item[\incorrect] Azure in Open (AIO)
\item[\correct] Visual Studio Enterprise (MPN) subscribers
\item[\correct] Visual Studio Professional
\item[\correct] Microsoft Partner Network
\item[\incorrect] Free Trial
\item[\correct] Pay-As-You-Go
\end{todolist}
\begin{center}\rule{6cm}{0.4pt}\end{center}