\section{The Certification}
\subsection{The Candidates}
Candidates for this exam are Microsoft Azure security engineers who implement security controls, maintain the security posture, manages identity and access, and protects data, applications, and networks. Candidates identify and remediate vulnerabilities by using a variety of security tools, implements threat protection, and responds to security incident escalations. As a Microsoft Azure security engineer, candidates often serve as part of a larger team dedicated to cloud-based management and security and may also secure hybrid environments as part of an end-to-end infrastructure.

Candidates for this exam should have strong skills in scripting and automation, a deep understanding of networking, virtualization, and cloud N-tier architecture, and a strong familiarity with cloud capabilities, Microsoft Azure products and services, and other Microsoft products and services.

\subsection{Content Overview}
\begin{itemize}
\item Manage identity and access (20-25\%)
	\begin{itemize}
	\item Configure Microsoft Azure Active Directory for workloads
	\item Configure Microsoft Azure AD Privileged Identity Management
	\item Configure Microsoft Azure tenant security
	\end{itemize}
\item Implement platform protection (35-40\%)
	\begin{itemize}
	\item Implement network security
	\item Implement host security
	\item Configure container security
	\item Implement Microsoft Azure Resource management security
	\end{itemize}
\item Manage security operations (15-20\%)
	\begin{itemize}
	\item Configure security services
	\item Configure security policies
	\item Manage security alerts
	\end{itemize}
\item Secure data and applications (30-35\%)
	\begin{itemize}
	\item Configure security policies to manage data
	\item Configure security for data infrastructure
	\item Configure encryption for data at rest
	\item Implement security for application delivery
	\item Configure application security
	\item Configure and manage Key Vault
	\end{itemize}
\end{itemize}

\clearpage
\subsection{Prerequisites}
The AZ-500 Azure Security Engineer Exam, like the MS-500 exam, covers a wide range of topics and technologies. Before considering taking this exam, you should first have good knowledge in the Azure technologies themselves which makes sense. You should learn what are the different Azure platform technologies in order to learn how to secure them.

So a good way to do that is to take the Azure AZ-900 (Azure Fundamentals) or the AZ-103 (Azure Administrator) exam first to learn more about Azure technologies. Now this is not a requirement for taking the AZ-500 exam, but it is a good start. If you are familiar with Azure technologies, then you can go and take the AZ-500 Azure Security Engineer Exam right away.

\subsection{The exam}
The AZ-500 Azure Security Engineer Exam expects you to know how to implement security controls, maintain the security posture, manages identity and access, and protects data, applications, and networks.

As per the AZ-500 Azure Security Engineer Exam official documentation:
\begin{formal}
Candidates identify and remediate vulnerabilities by using a variety of security tools, implements threat protection, and responds to security incident escalations. As a Microsoft Azure security engineer, candidates often serve as part of a larger team dedicated to cloud-based management and security and may also secure hybrid environments as part of an end-to-end infrastructure
\end{formal}